material and methods

### 2017-08-21 man/ms_0_intro.Rmd
update mat and methods

>>>>

### 
Uso de NDVI como estimador de la NPP:

* The NDVI properties have allowed the use of this information for estimating the Net Primary Production (NPP) (Goward and Dye, 1987; Running et al., 2004; Hasenauer et al., 2012). Different studies have already found a strong relationship between NPP and radial growth (e.g., Granier et al., 2008; Babst et al., 2013, 2014a, 2014b; Vicente-Serrano et al., 2015), albeit with significant differences, particularly those related to species, sites and environmental conditions.

* Ver Gilaber et al. 2017 http://www.mdpi.com/2072-4292/9/3/193

### 2017-08-21 man/ms_1_material_methods.Rmd
update mat and methods

## NDVI

@@

----- 
:red_circle: `duda aqui` Varias referencias hablan de los años 2005 y 2012 como  extremadamente secos. Pero habría que hacer alguna referencia y/o análisis. Tengo dudas de si hemos de analizar (e incluir) que efectivamente los años 2005 y 2012 fueron caracterizados por un extrema sequía, por lo que habría que  incluyendo referencia a apéndice 
-----

@@

* Meter aquí algunos datos de sequñia, similar a lo planteado por Gazol

@@

@@

Resilience

@@

>>>>

@@

----- 
:red_circle: `duda aqui` Varias referencias hablan de los años 2005 y 2012 como  extremadamente secos. Pero habría que hacer alguna referencia y/o análisis. Tengo dudas de si hemos de analizar (e incluir) que efectivamente los años 2005 y 2012 fueron caracterizados por un extrema sequía, por lo que habría que  incluyendo referencia a apéndice

* O quizá un apartado llamado Drought episodes (similar a esto https://www.nature.com/articles/srep28269)
-----

@@

* Meter aquí algunos datos de sequia, similar a lo planteado por Gazol

@@

To characterize the vegetation greeness we used the Enhanced Vegetation Index (EVI) derived from MOD13Q1 product obtained by the Moderate Resolution Imaging Spectroradiometer (MODIS) sensor [@Didan2015]. EVI product consits of 16-day maximun value composite images (23 per year) of the EVI value with a spatial resolution of 231 m x 231 m.

EVI junto con NDVI ha sido utilizado para cuantificar la productividad primaria ... No obstante we used EVI instead of NDVI because it is more sensitive to change in high-biomass areas; EVI reduces the influence of atmospheric conditions on vegetation index values, and EVI corrects for canopy background signals [@Huete2002, @Krapivin2015].

NDVI sirve para estimar la producción primaria neta. Existen diferentes estudio que han evaluado el efecto de la sequía sobre la producción primaria neta utilizando NDVI.

Data were obtained using a Google Earth Engine script (:red_circle: cite gists) for the 2000 - 2015 period. The EVI data are geometrically and atmospherically corrected and include information about the quality ass.... 
:red_circle:

These data are geometrically and atmospherically corrected, and include an index of data quality (reliability, which range from 0 – good quality data – to 4 – raw data or absent for different reasons) based on the environmental conditions in which the data was recorded

We first used the Quality Assesment (QA band) information of this product to filter out those values affected by high content of aerosols, clouds, shadows, snow or water; and then a quality assessment was carried out to filter the ... [@Reyes2015]

:red_circle: reescribir esto de la calidad.

After the filter out process, we built the annual EVI profile for each pixel and then computed the EVI's annual mean values and the EVI anomaly for each pixel for the period 2000 - 2015.

@@

## Resilience

To evaluate the effects of the drought events on greeennes and tree growth we used the four different resilience metrics [@Lloret2011]

@@

* Evaluación de la resiliencia en cada variable 
* Long-term trends in RW
* Anomalías en EVI??
